A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-07-07 07_Manuscript.Rmd
Add a few comments and minor copy-edits to manuscript

Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as a sole powdery mildew management strategy. <!-- Citation needed -->
Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013].
In Australia, quantitative resistance has also been incorporated into few commercially available varieties.
Jade-AU <!-- Need PBR emblem here --> has the the best disease resistance to powdery mildew (moderately susceptible).
Because cultivar choice does not confer complete resistance to powdery mildew, additional strategies such as fungicide treatments are necessary to limit yield loss when conditions for the disease are conducive.

@@

A categorical disease pressure factor was created by binning trials based on the mean AUDPC of the no spray control plot into two levels: 'low disease pressure' or 'high disease pressure'.
The two levels were separated via the median AUDPC (153.63) of the no spray control plots.

@@

This analysis use the grain yield standardised mean difference (SMD) as the response variable. 
SMD were chosen to reduce the inherent variability between trials due to location and seasonal effects on grain yields.  
$SMD = \frac{Y_i-\overline{Y_c}}{\sigma_p}$ [@HigginsGreen]  
Where $Y_i$ is the treatment mean, $Y_c$ is the no spray control treatment mean and $\sigma_p$ is the trial pooled standard deviation.

@@

@@

Fungicide application costs in Australia are relatively cheap.
We estimate these costs to be approximately \$20&nbsp;AU per hectare.
Lucrative returns of up to \$2260&nbsp;AU per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than necessary.
Excessive use of fungicides are not only costly, but lead to problems such as fungicide resistance.
_Podosphaera xanthii_ is categorised by the Australian Fungicide resistance Action Committee (FRAC) as a 'High risk' candidate to evolve fungicide resistance.
Prior experiences confirm that the evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with potential fungicide resistance in mind.
Powdery mildew is one such group of fungal pathogens with an extensive track record of rapidly developing fungicide resistance.
In cucurbits, it evolved resistance to benzimidazole within three years of its registration [@Peterson1973] and has evolved resistance to numerous fungicide classes, such as benzimidazoles, demethylation inhibitors, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines since [@Mcgrath2001].
In cereal crops _Blumeria graminis_ showed reduced sensitivity to strobilurins in 1998, two years after the fungicides began being used in Europe [@Chin2001].

>>>>

Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy. <!-- Citation needed -->
Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013].
In Australia, quantitative resistance has also been incorporated into few commercially available varieties.
Jade-AU <!-- Need PBR emblem here --> has the the best disease resistance to powdery mildew (moderately susceptible).
Because cultivar choice does not confer complete resistance to powdery mildew, additional strategies such as fungicide treatments are necessary to limit yield loss when conditions for the disease are conducive.

@@

A categorical disease pressure factor was created by binning trials based on the mean AUDPC of the no spray control plot into two levels: 'low disease pressure' or 'high disease pressure'.
The two levels were separated via the median AUDPC <!-- Should this be encoded not hard coded in case it changes? -->(153.63) of the no spray control plots.

@@

This analysis uses the grain yield standardised mean difference (SMD) as the response variable. 
SMD were chosen to reduce the inherent variability between trials due to location and seasonal effects on grain yields.
$SMD = \frac{Y_i-\overline{Y_c}}{\sigma_p}$ [@HigginsGreen]
Where $Y_i$ is the treatment mean, $Y_c$ is the no spray control treatment mean and $\sigma_p$ is the trial pooled standard deviation.

@@

Overall the meta-analysis indicated that, with the exception of `Early` single sprays all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure 1).
Treatments incorporating multiple fungicide applications, `recommendedPlus` and `LatePlus` produced the highest yield protection estimates at 196 and 220&nbsp;kg&nbsp;/&nbsp;ha respectively (Table 3). 
Both `RecommendedPlus` and `LatePlus` were also significantly higher than single applications starting `Early` (P = 0.008 and P = 0.003 respectively) and `Late`(P = 0.05 and P = 0.03 respectively). 
Within the single fungicide application treatments `recommended` provided the highest yield protection, and was estimated at saving an average of 160 kg / ha relative to the no spray control (P < 0.0001). `recommended` treatments were was also significantly higher than `Early` treatments by 122 kg / ha (P = 0.004).

The $Q_M$ omnibus test of moderators, shows the moderators significantly influence the model ($Q_M = 26.22, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 568.31, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators, which might influence grain yield.

A log-ratio test, based on a chi-squared distribution, indicated that retaining the `SpraySchedule` variable as a random interactive term provided a significantly better model (P = 0.0179).

```{r table3_Contrasts}
T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
T3 %>%
   kable()
```

@@

Fungicide application costs in Australia are relatively cheap.
We estimate these costs to be approximately \$20&nbsp;AU per hectare.
Lucrative returns of up to \$2260&nbsp;AU per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew when they are unnecessary.
Excessive use of fungicides are not only costly, but lead to problems such as fungicide resistance.
_Podosphaera xanthii_ is categorised by the Australian Fungicide resistance Action Committee (FRAC) as a 'High risk' candidate to evolve fungicide resistance.
Prior experiences confirm that the evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with potential fungicide resistance in mind.
Powdery mildew is one such group of fungal pathogens with an extensive track record of rapidly developing fungicide resistance.
In cucurbits, it evolved resistance to benzimidazole within three years of its registration [@Peterson1973] and has evolved resistance to numerous fungicide classes, such as benzimidazoles, demethylation inhibitors, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines since [@Mcgrath2001].
In cereal crops _Blumeria graminis_ showed reduced sensitivity to strobilurins in 1998, two years after the fungicides began being used in Europe [@Chin2001].
